# Simple linear regression

## playbill
First we load the data.

```{r}
playbill <- read_csv("http://www.stat.tamu.edu/~sheather/book/docs/datasets/playbill.csv")
```

Then we fit a linear model, $Y=\beta_0 + \beta_1 + e$
and summarize it in Table \@ref(tab:pb_fit1).

```{r, pb_fit1}
pb_fit1 <- lm(CurrentWeek ~ LastWeek, data = playbill)
kable(summary(pb_fit1)$coef,
      booktabs = TRUE,
      caption = "Coefficients our linear model.")
```

### a {-}
The confidence intervals for $\beta_1$ are given by

```{r}
confint(pb_fit1)[2, ]
```

As per the question, 1 seems like a plausible value given that returns are
likely to be similar from one week to another (although exactly 1
is incredibly unlikely).

### b {-}
We proceed to test the hypotheses
$$
\begin{gather}
H_0:\beta_0 = 10000 \\
H_1:\beta_0 \neq 10000
\end{gather}
$$

by running

```{r}
h_0 <- 10000
h_obs <- coef(pb_fit1)[[1]]
h_obs_se <- summary(pb_fit1)$coef[1, 2]

tobs <- (h_obs - h_0) / h_obs_se
(pobs <- 2 * pt(abs(tobs), nrow(playbill) - 2, lower.tail = FALSE))
```

which leads us to accept the null hypothesis, $t(16) = `r pobs`$.

### c {-}
We make a prediction, including prediction interval, for a 400,000\$$ box
office result in the previous week:

```{r}
predict(pb_fit1, data.frame(LastWeek = 400000), interval = "prediction")
```

A prediction of 450,000\$$ is **not** feasible, given it is far outside
our that our 95% prediction interval. 

### d {-}
This seems like an okay rule given the almost-perfect correlation from one
week to another; however, looking at the residuals we see that there are at
least three values that are predicted badly (Figure \@ref(fig:pb-resid))

```{r pb-resid}
par(mfrow = c(2, 2))
plot(pb_fit1)
```

