# Simple linear regression

## playbill
First we load the data.

```{r, message = FALSE}
playbill <- read_csv(file.path("data", "playbill.csv"))
```

Then we fit a linear model, $Y=\beta_0 + \beta_1 + e$
and summarize it in Table \@ref(tab:pb-fit1).

```{r, pb-fit1}
pb_fit1 <- lm(CurrentWeek ~ LastWeek, data = playbill)
kable(summary(pb_fit1)$coef,
      booktabs = TRUE,
      caption = "Coefficients our linear model.")
```

### a {-}
The confidence intervals for $\beta_1$ are given by

```{r}
confint(pb_fit1)[2, ]
```

As per the question, 1 seems like a plausible value given that returns are
likely to be similar from one week to another (although exactly 1
is incredibly unlikely).

### b {-}
We proceed to test the hypotheses
$$
\begin{gather}
H_0:\beta_0 = 10000 \\
H_1:\beta_0 \neq 10000
\end{gather}
$$

by running

```{r}
h_0 <- 10000
h_obs <- coef(pb_fit1)[[1]]
h_obs_se <- summary(pb_fit1)$coef[1, 2]

tobs <- (h_obs - h_0) / h_obs_se
(pobs <- 2 * pt(abs(tobs), nrow(playbill) - 2, lower.tail = FALSE))
```

which leads us to accept the null hypothesis, $t(16) = `r tobs`$, $p = `r pobs`$.

### c {-}
We make a prediction, including prediction interval, for a 400,000\$ box
office result in the previous week:

```{r}
predict(pb_fit1, data.frame(LastWeek = 400000), interval = "prediction")
```

A prediction of 450,000\$ is **not** feasible, given it is far outside
our 95% prediction interval. 

### d {-}
This seems like an okay rule given the almost-perfect correlation from one
week to another; however, looking at the residuals we see that there are at
least three values that are predicted badly (Figure \@ref(fig:pb-resid))

```{r pb-resid, fig.cap = "Residuals for our linear fit to the playbill data."}
par(mfrow = c(2, 2))
plot(pb_fit1)
```

## Indicators

```{r, message = FALSE}
indicators <- read_csv(file.path("data", "indicators.txt"))
```

We begin by fitting our linear model to the data (Table \@ref(tab:indicators-summary)).

```{r, indicators-summary}
ind_fit1 <- lm(PriceChange ~ LoanPaymentsOverdue, data = indicators)
kable(summary(ind_fit1)$coef,
      booktabs = TRUE,
      caption = "Coefficients for our linear model to the indicators data set.")
```

### a {-}
The 95% confidence interval for the $\beta_1$ estimate is, as before:

```{r}
confint(ind_fit1)[2, ]
```

There is reason to believe that there is a negative trend.

### b {-}
We now create a confidence interval for $\text{E}[Y|X=4]$:

```{r}
predict(ind_fit1, data.frame(LoanPaymentsOverdue = 4), interval = "confidence")
```

0% is not a reasonable estimate for $\text{E}[Y|X=4]$ since the 95% confidence
limit is far below 0.

## Invoices

### a {-}
We first find a 95% confidence level for $\beta_0$ using the output printed in
the book.

```{r}
beta0 <- 0.6417099
beta0_se <- 0.122707
beta0_t <- 5.248
beta0_margin <- 1.96 * beta0_se
(beta0_95 <- c(beta0 - beta0_margin, beta0 + beta0_margin))
```

Thus, the confidence limit it `r beta0_95`

### b {-}





